Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2025-03-07 Manuscript/src/sections/appendix.tex
submission: published version

In this section, we show the results of the analysis of the dataset with air speed measurements at three heights.
% todo check manually
Only \num{3059} entries in the \ac{db2} had air speed measurements at three heights with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
A summary of the papers that collected these data is provided in Table~\ref{tab:three_heights_papers}.
The table also shows the number of measurements for each paper and how much (percentage) each study contributed to the dataset.
\begin{table}[htb!]
    \centering
    \input{tables/publications_with_three_heights.tex}
    \caption{The number of entries used in this analysis, grouped by publication.
    We did not include papers with less than \num{5} entries.}
    \label{tab:three_heights_papers}
\end{table}
The paper by Cena et al.\ (1999), de Dear et al.\ (1994), and Zhang et al.\ (2013 and 2010) contributed the most to the dataset (\qty{79}{\percent}).
The air speed distribution at the three heights for each paper is shown in Figure~\ref{fig:boxenplot_wind_speed_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/boxenplot_wind_speed_three_heights}
    \caption{Measured air speeds distribution at three heights and relative air speed adjusted based on the \ac{met} value.
    We did not include papers with less than \num{5} entries.
    We are also not showing the outliers.}
    \label{fig:boxenplot_wind_speed_three_heights}
\end{figure}
The adjustment of \ac{vr} based on the \ac{met} significantly increased the base value of the air speed measured by all the studies.
With the value of \ac{vr} being \var{delta_v_mean} higher than the average of the other air speeds combined.
The discussion on whether this increase is justified is beyond the scope of this paper, since both standards require the user to adjust the air speed based on the \ac{met} value using the same equation.

@@

We, however, plotted the \ac{pmv} and \ac{pmv-ce} values against the \ac{tsv} values and we plotted the \ac{lowess} curves to visualize the prevailing data trend.
The results are shown in Figure~\ref{fig:bubble_models_vs_tsv_three_heights}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv_three_heights}
    \caption{Comparison between the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights. 
    The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data for the dataset with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} and measured at three heights.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.
    The brown dashed line represents the identity line, where the slope is 1 and the intercept is 0.}
    \label{fig:bubble_models_vs_tsv_three_heights}
\end{figure*}
The \ac{pmv} model is more accurate than the \ac{pmv-ce} model.
The intercept of the \ac{pmv} model is \var{intercept_v_02_three_pmv} while the intercept of the \ac{pmv-ce} model is \var{intercept_v_02_three_pmv_ce}.
Moreover, the \ac{pmv-ce} \ac{lowess} curve is only marginally higher than \num{0} despite participants reporting a \ac{tsv} of \num{3}.

The overall bias of the \ac{pmv} and \ac{pmv-ce} models is shown in Figure~\ref{fig:hist_discrepancies_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies_three_heights}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights.}
    \label{fig:hist_discrepancies_three_heights}
\end{figure}
% todo check manually
The \ac{pmv} model has a bias of \num{-.39} while the \ac{pmv-ce} model has a bias of \num{-.38}.
These results allow us to conclude that the \ac{pmv} has a similar accuracy to the \ac{pmv-ce} model for the dataset with air speed measured at three heights.

>>>>

In this section, we show the results of the analysis of the dataset with air speed measurements at three heights.
Only \num{3059} entries in the \ac{db2} had air speed measurements at three heights with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
A summary of the papers that collected these data is provided in Table~\ref{tab:three_heights_papers}.
The table also shows the number of measurements for each paper and how much (percentage) each study contributed to the dataset.
\begin{table}[htb!]
    \centering
    \input{tables/publications_with_three_heights.tex}
    \caption{The number of entries used in this analysis, grouped by publication.
    We did not include papers with less than \num{5} entries.}
    \label{tab:three_heights_papers}
\end{table}
The paper by Cena et al.\ (1999), de Dear et al.\ (1994), and Zhang et al.\ (2013 and 2010) contributed the most to the dataset (\qty{79}{\percent}).
The air speed distribution at the three heights for each paper is shown in Figure~\ref{fig:boxenplot_wind_speed_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/boxenplot_wind_speed_three_heights}
    \caption{Measured air speeds distribution at three heights and relative air speed adjusted based on the \ac{met} value.
    We did not include papers with less than \num{5} entries.
    We are also not showing the outliers.}
    \label{fig:boxenplot_wind_speed_three_heights}
\end{figure}
The adjustment of \ac{vr} based on the \ac{met} significantly increased the base value of the air speed measured by all the studies.
With the value of \ac{vr} being \var{delta_v_mean} higher than the average of the other air speeds combined.
The discussion on whether this increase is justified is beyond the scope of this paper, since both standards require the user to adjust the air speed based on the \ac{met} value using the same equation.

@@

We, however, plotted the \ac{pmv} and \ac{pmv-ce} values against the \ac{tsv} values and we plotted the \ac{lowess} curves to visualize the prevailing data trend.
The results are shown in Figure~\ref{fig:bubble_models_vs_tsv_three_heights}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv_three_heights}
    \caption{Comparison between the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights. 
    The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data for the dataset with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} and measured at three heights.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.
    The brown dashed line represents the identity line, where the slope is 1 and the intercept is 0.}
    \label{fig:bubble_models_vs_tsv_three_heights}
\end{figure*}
The \ac{pmv} model is more accurate than the \ac{pmv-ce} model.
The intercept of both \ac{pmv} models is \var{intercept_v_02_three_pmv_ce}.
Moreover, the \ac{pmv-ce} \ac{lowess} curve is only marginally higher than \num{0} despite participants reporting a \ac{tsv} of \num{3}.

The overall bias of the \ac{pmv} and \ac{pmv-ce} models is shown in Figure~\ref{fig:hist_discrepancies_three_heights}.
\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies_three_heights}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models for the dataset with air speed measured at three heights.}
    \label{fig:hist_discrepancies_three_heights}
\end{figure}
The \ac{pmv} model has a bias of \num{-.39} while the \ac{pmv-ce} model has a bias of \num{-.38}.
These results allow us to conclude that the \ac{pmv} has a similar accuracy to the \ac{pmv-ce} model for the dataset with air speed measured at three heights.

### 2025-03-07 Manuscript/src/sections/results.tex
submission: published version

Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0}
    \end{subfigure}
    \par\bigskip % force a bit of vertical whitespace
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0.2}
    \end{subfigure}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants.
    In a) and b) for the entire dataset, while in c and d for the dataset when \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
    In a) and c) are shown the results for the \ac{pmv} model, and in b) and d) for the \ac{pmv-ce} model.
    The number of data points in each bin of the two charts at the top (a and b) and at the bottom (c and d) is the same, and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart, while the model accuracy of predicting participants grouped by their \ac{tsv} is shown over each bar.
    A random model would have an accuracy of \qty{14}{\percent}.}
    \label{fig:bar_stacked_model_accuracy}
\end{figure}
Both \ac{pmv} formulations underestimate the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracies of the \ac{pmv} and \ac{pmv-ce} are \var{overall_acc_pmv} and \var{overall_acc_pmv_ce}, respectively, when using the whole dataset.
The overall accuracy of both \ac{pmv} models changed to \var{overall_acc_pmv_0.2} and \var{overall_acc_pmv_ce_0.2}, respectively when only considering entries with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
% todo check data manually
The \ac{pmv-ce} model outperforms the \ac{pmv} model for \ac{tsv}~=~0 and -1.
However, the \ac{pmv} model outperforms the \ac{pmv-ce} model when considering \ac{tsv}~=~1.
The number of data points in each \ac{tsv} bin is different.
\mycite{Cheung2019} grouped people based on the same heat loss or gains (same \ac{pmv} ranges), not the same \ac{tsv} as we did here, and then quantified the sensitivity of the model, i.e., how many times the \ac{pmv} model correctly predicted \ac{tsv}.
They found that the accuracy of \ac{pmv} in predicting \ac{tsv} was only \qty{34}{\percent} \mycite{Cheung2019}.

@@

In Table~\ref{tab:f1}, we report the F1 scores for both models, i) using the whole dataset, ii) only keeping entries with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}, iii) only keeping data points that have \ac{vr} measured at three heights with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}, and iv) for those with a $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
\begin{table}[htb!]
    \centering
    \input{tables/f1}
    \caption{F1 scores for the \ac{pmv} and \ac{pmv-ce} models for different subsets of data.}
    \label{tab:f1}
\end{table}
% todo check data manually
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}) for all data.
For the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} the F1-macro scores of the \ac{pmv} and \ac{pmv-ce} models only slightly improved.
We then analyzed the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} and with \ac{vr} measured at three heights.
The score of the \ac{pmv-ce} decreased (F1-macro~=~\num{0.16}) and it is lower than the value for the \ac{pmv} (F1-macro~=~\num{0.17}).
Our results show that the assumption that the \ac{pmv-ce} better takes into account the effect of elevated air speed is false.
All the F1 scores significantly increase when analyzing the dataset with $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
This highlights that the \ac{pmv} models are only accurate in predicting the thermal sensation of people when the thermal sensation is close to neutral.

\subsection{Model Bias}\label{subsec:model-bias}
The intended aim of the \ac{pmv} model is not to accurately predict individual thermal responses from participants.
The \ac{pmv} model was developed to predict the average thermal sensation of an undefined large group of occupants sharing the same environment.
The results presented so far are primarily comparing individual \ac{tsv} to \ac{pmv}.
This type of analysis does not conclusively disprove the inefficacy of the \ac{pmv} models in predicting the average thermal sensation of a large group of occupants.
Moreover, grouping the results into discrete categories introduces rounding errors since some participants reported \ac{tsv} on a continuous scale and the \ac{pmv} value is a continuous variable.
To compensate for this, we plotted the \ac{pmv} and \ac{pmv-ce} values as a function of \ac{tsv} in Figure~\ref{fig:bubble_models_vs_tsv} and we plotted a \ac{lowess} curve.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv}
    \caption{The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.
    The brown dashed line represents the identity line where the slope is 1 and the intercept is 0.}
    \label{fig:bubble_models_vs_tsv}
\end{figure*}
The curve, in the Figure, is calculated using the individual data and not the binned data.
We only binned the data to aid the visualization of a large dataset.
For the model to accurately predict people’s thermal sensation, the regression line (black continuous line) should pass through the origin of the Cartesian plane and have a slope of 1.
This ideal prediction is referred to as the identity line, shown as the brown dashed line in the figure.
The intercepts for the \ac{pmv} is \var{intercept_all_pmv} and for the \ac{pmv-ce} is \var{intercept_all_pmv_ce} which means that the model has a bias of less than one-quarter of a thermal sensation interval.
% todo check data manually
This result is aligned with those presented in Figure~\ref{fig:bar_stacked_model_accuracy} where the \ac{pmv} and \ac{pmv-ce} models can predict people who reported to be neutral \qty{51}{\percent} and \qty{58}{\percent} of the times, respectively.
Both \ac{pmv} formulations always under-predict the thermal sensation of people who reported to be on the extremes of the \ac{tsv};
the slope of the curve is significantly lower than 1.

\subsubsection{Model Overall Bias}\label{subsubsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and \ac{pmv-ce} predictions from the self-reported \ac{tsv}.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics.
% todo check data manually
Overall, both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{Overall bias of the \ac{pmv} and \ac{pmv-ce} models for the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
    The x-axis shows the discrepancy (bias) between the predicted and self-reported \ac{tsv}.
    We have binned the data into intervals of equal width.
    We colored the bars in the range from \numrange{-.5}{.5} to highlight the number of responses that are within this range.
    We report the median and inter-quantile ranges since data are not normally distributed.
    }
    \label{fig:hist_discrepancies}
\end{figure*}
When including only the data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} the median bias of the \ac{pmv} model reduces to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improves.
The median bias for the \ac{pmv-ce} also decreases to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0} but it is higher than the one for the \ac{pmv}.

\subsubsection{Model Bias as Function of Five Input Variables}\label{subsubsec:model-bias-variable}
Here we present the model bias as a function of \ac{tdb}, \ac{vr}, \ac{rh}, and \ac{met}.
Results are shown in Figure~\ref{fig:bias_models}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bias_models}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models plotted as a function of the input variables.
    The x ticks labels show the bin range.
    The square bracket($]$) means that the right value is included in the range.
    The red dashed lines show the acceptable range of bias.
    Each bin has a different number of data points.
    }
    \label{fig:bias_models}
\end{figure*}
In each sub-figure, we have binned the results into discrete intervals.
The x-axis tick label shows the bin range.
All the boxen plots have the same area to aid visualization, even though the number of points in each bin is not constant.
The results depict that the use of the \ac{pmv-ce} model does not improve the bias of the \ac{pmv} results across all input variables.
% todo check data manually
On the contrary, the bias of the \ac{pmv-ce}~=~\num{-.33} is higher than \ac{pmv}~=~\num{-0.23} for \qty{0.3}{\m\per\s}~$<$~\ac{vr}~$\leq$~\qty{0.46}{\m\per\s}.
Both models have a median bias higher or equal to $\lvert0.5\lvert$ for \ac{tdb}~$\leq$~\qty{21}{\celsius}.

>>>>

Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0}
    \end{subfigure}
    \par\bigskip % force a bit of vertical whitespace
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0.2}
    \end{subfigure}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants.
    In a) and b) for the entire dataset, while in c and d for the dataset when \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
    In a) and c) are shown the results for the \ac{pmv} model, and in b) and d) for the \ac{pmv-ce} model.
    The number of data points in each bin of the two charts at the top (a and b) and at the bottom (c and d) is the same, and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart, while the model accuracy of predicting participants grouped by their \ac{tsv} is shown over each bar.
    A random model would have an accuracy of \qty{14}{\percent}.}
    \label{fig:bar_stacked_model_accuracy}
\end{figure}
Both \ac{pmv} formulations underestimate the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracies of the \ac{pmv} and \ac{pmv-ce} are \var{overall_acc_pmv} and \var{overall_acc_pmv_ce}, respectively, when using the whole dataset.
The overall accuracy of both \ac{pmv} models changed to \var{overall_acc_pmv_0.2} and \var{overall_acc_pmv_ce_0.2}, respectively when only considering entries with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
The \ac{pmv-ce} model outperforms the \ac{pmv} model for \ac{tsv}~=~0 and -1.
However, the \ac{pmv} model outperforms the \ac{pmv-ce} model when considering \ac{tsv}~=~1.
The number of data points in each \ac{tsv} bin is different.
\mycite{Cheung2019} grouped people based on the same heat loss or gains (same \ac{pmv} ranges), not the same \ac{tsv} as we did here, and then quantified the sensitivity of the model, i.e., how many times the \ac{pmv} model correctly predicted \ac{tsv}.
They found that the accuracy of \ac{pmv} in predicting \ac{tsv} was only \qty{34}{\percent} \mycite{Cheung2019}.

@@

In Table~\ref{tab:f1}, we report the F1 scores for both models, i) using the whole dataset, ii) only keeping entries with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}, iii) only keeping data points that have \ac{vr} measured at three heights with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}, and iv) for those with a $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
\begin{table}[htb!]
    \centering
    \input{tables/f1}
    \caption{F1 scores for the \ac{pmv} and \ac{pmv-ce} models for different subsets of data.}
    \label{tab:f1}
\end{table}
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}) for all data.
For the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} the F1-macro scores of the \ac{pmv} and \ac{pmv-ce} models only slightly improved.
We then analyzed the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} and with \ac{vr} measured at three heights.
The score of the \ac{pmv-ce} decreased (F1-macro~=~\num{0.16}) and it is lower than the value for the \ac{pmv} (F1-macro~=~\num{0.17}).
Our results show that the assumption that the \ac{pmv-ce} better takes into account the effect of elevated air speed is false.
All the F1 scores significantly increase when analyzing the dataset with $\lvert \textrm{PMV}\lvert \leq 1.5$ and $\lvert \textrm{TSV}\lvert \leq 1.5$.
This highlights that the \ac{pmv} models are only accurate in predicting the thermal sensation of people when the thermal sensation is close to neutral.

\subsection{Model Bias}\label{subsec:model-bias}
The intended aim of the \ac{pmv} model is not to accurately predict individual thermal responses from participants.
The \ac{pmv} model was developed to predict the average thermal sensation of an undefined large group of occupants sharing the same environment.
The results presented so far are primarily comparing individual \ac{tsv} to \ac{pmv}.
This type of analysis does not conclusively disprove the inefficacy of the \ac{pmv} models in predicting the average thermal sensation of a large group of occupants.
Moreover, grouping the results into discrete categories introduces rounding errors since some participants reported \ac{tsv} on a continuous scale and the \ac{pmv} value is a continuous variable.
To compensate for this, we plotted the \ac{pmv} and \ac{pmv-ce} values as a function of \ac{tsv} in Figure~\ref{fig:bubble_models_vs_tsv} and we plotted a \ac{lowess} curve.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bubble_models_vs_tsv}
    \caption{The \ac{lowess} curve shows the relationship between the raw \ac{pmv} and \ac{tsv} data.
    Raw data were then binned and a bubble chart (circle area is proportional to the number of votes in that bin) was superimposed over the regression curve to aid the visualization of a large dataset.
    The brown dashed line represents the identity line where the slope is 1 and the intercept is 0.}
    \label{fig:bubble_models_vs_tsv}
\end{figure*}
The curve, in the Figure, is calculated using the individual data and not the binned data.
We only binned the data to aid the visualization of a large dataset.
For the model to accurately predict people’s thermal sensation, the regression line (black continuous line) should pass through the origin of the Cartesian plane and have a slope of 1.
This ideal prediction is referred to as the identity line, shown as the brown dashed line in the figure.
The intercepts for the \ac{pmv} is \var{intercept_all_pmv} and for the \ac{pmv-ce} is \var{intercept_all_pmv_ce} which means that the model has a bias of less than one-quarter of a thermal sensation interval.
This result is aligned with those presented in Figure~\ref{fig:bar_stacked_model_accuracy} where the \ac{pmv} and \ac{pmv-ce} models can predict people who reported to be neutral \qty{51}{\percent} and \qty{58}{\percent} of the times, respectively.
Both \ac{pmv} formulations always under-predict the thermal sensation of people who reported to be on the extremes of the \ac{tsv};
the slope of the curve is significantly lower than 1.

\subsubsection{Model Overall Bias}\label{subsubsec:model-overall-bias}
We calculated the overall bias of the model as previously done by \mycite{Humphreys2002} by subtracting the \ac{pmv} and \ac{pmv-ce} predictions from the self-reported \ac{tsv}.
Figure~\ref{fig:hist_discrepancies} contains the summary statistics.
Overall, both the \ac{pmv} and \ac{pmv-ce} models have a median bias lower than half of a thermal sensation interval.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/hist_discrepancies}
    \caption{Overall bias of the \ac{pmv} and \ac{pmv-ce} models for the subset of data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s}.
    The x-axis shows the discrepancy (bias) between the predicted and self-reported \ac{tsv}.
    We have binned the data into intervals of equal width.
    We colored the bars in the range from \numrange{-.5}{.5} to highlight the number of responses that are within this range.
    We report the median and inter-quantile ranges since data are not normally distributed.
    }
    \label{fig:hist_discrepancies}
\end{figure*}
When including only the data with \ac{vr}~$\geq$~\qty{0.2}{\m\per\s} the median bias of the \ac{pmv} model reduces to \var{bias_median_pmv_0.2} from \var{bias_median_pmv_0}, meaning that at higher speed the \ac{pmv} model improves.
The median bias for the \ac{pmv-ce} also decreases to \var{bias_median_pmv_ce_0.2} from \var{bias_median_pmv_ce_0} but it is higher than the one for the \ac{pmv}.

\subsubsection{Model Bias as Function of Five Input Variables}\label{subsubsec:model-bias-variable}
Here we present the model bias as a function of \ac{tdb}, \ac{vr}, \ac{rh}, and \ac{met}.
Results are shown in Figure~\ref{fig:bias_models}.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bias_models}
    \caption{Bias of the \ac{pmv} and \ac{pmv-ce} models plotted as a function of the input variables.
    The x ticks labels show the bin range.
    The square bracket($]$) means that the right value is included in the range.
    The red dashed lines show the acceptable range of bias.
    Each bin has a different number of data points.
    }
    \label{fig:bias_models}
\end{figure*}
In each sub-figure, we have binned the results into discrete intervals.
The x-axis tick label shows the bin range.
All the boxen plots have the same area to aid visualization, even though the number of points in each bin is not constant.
The results depict that the use of the \ac{pmv-ce} model does not improve the bias of the \ac{pmv} results across all input variables.
On the contrary, the bias of the \ac{pmv-ce}~=~\num{-.33} is higher than \ac{pmv}~=~\num{-0.23} for \qty{0.3}{\m\per\s}~$<$~\ac{vr}~$\leq$~\qty{0.46}{\m\per\s}.
Both models have a median bias higher or equal to $\lvert0.5\lvert$ for \ac{tdb}~$\leq$~\qty{21}{\celsius}.
